Pulling oral and IV data from CvTdb

### 2023-01-05 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Change variable names for newly corrected & normalized variables to make them clearer (correct.dose_level_normalized -> studies.dose_level_normalized_corrected, conc_time_values.conc_sd -> conc_time_values.conc_sd_normalized)

```{r}
tmp[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

@@

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc,
                 shape = factor(documents_extraction.id),
                 color = as.numeric(correct.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc/as.numeric(correct.dose_level_normalized),
                 shape = factor(documents_extraction.id),
                 color = as.numeric(correct.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

@@

```{r}
cvt_data[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
      studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
```

@@

```{r}
cvt_data[series.conc_units_original == "ug/L",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]

cvt_data[series.conc_units_original == "ug/mL",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original]

cvt_data[series.conc_units_original == "mg/L",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original]

cvt_data[series.conc_units_original == "ug/dL",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-4]

cvt_data[series.conc_units_original == "ng/mL",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]

cvt_data[series.conc_units_original == "pg/mL",
         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-6]

>>>>

```{r}
tmp[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

@@

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc,
                 shape = factor(documents_extraction.id),
                 color = as.numeric(studies.dose_level_normalized_corrected))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc/as.numeric(studies.dose_level_normalized_corrected),
                 shape = factor(documents_extraction.id),
                 color = as.numeric(studies.dose_level_normalized_corrected))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

@@

```{r}
cvt_data[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
      studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
```

@@

```{r}
cvt_data[series.conc_units_original == "ug/L",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]

cvt_data[series.conc_units_original == "ug/mL",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]

cvt_data[series.conc_units_original == "mg/L",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]

cvt_data[series.conc_units_original == "ug/dL",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-4]

cvt_data[series.conc_units_original == "ng/mL",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]

cvt_data[series.conc_units_original == "pg/mL",
         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-6]
